Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-21 paper.tex
intro footnotes

The rest of the paper is structured as follows: 
in Section~\ref{sec:background} the technologies used are explained;
Section~\ref{sec:state} summarizes previous work in this field; 
Section~\ref{sec:motivation} states the motivation to carry out this work;
all the effort made using AWS is explained in Section~\ref{sec:workingaws};
while the effort made in Openstack is described in Section~\ref{sec:openstack};
finally Section~\ref{sec:conclusions} gives an overview of the advances made and~\ref{sec:future} propose the next steps
should be take in this research.

@@

\section{\uppercase{GPGPU Shared Service in OpenStack}}
In this section all the work related to OpenStack that has been done is explained, from the development of an external module to handle remote GPUs to the physical setup and its testing.

>>>>

The rest of the paper is structured as follows: 
in Section~\ref{sec:background} the technologies used are explained;
Section~\ref{sec:state} summarizes previous work in this field; 
Section~\ref{sec:motivation} states the motivation to carry out this work;
all the effort made using AWS is explained in Section~\ref{sec:workingaws};
while the effort made in Openstack is described in Section~\ref{sec:gpgpuOS};
finally Section~\ref{sec:conclusions} gives an overview of the advances made and~\ref{sec:future} propose the next steps
should be take in this research.

@@

\section{\uppercase{GPGPU Shared Service in OpenStack}}
\label{sec:gpgpuOS}
In this section all the work related to OpenStack that has been done is explained, from the development of an external module to handle remote GPUs to the physical setup and its testing.
